A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-06-26 tex-arxiv/article.tex
some wording fixes in results

As illustrated in fig. \ref{fig:vis_exec}, model outputs were visualized to use their qualitative aspects in guiding hyperparameter choice and a preliminary implementation on a real robot was also achieved -- executing throws with some sampled trajectories generated by the simpler feedforward network. As can be seen, when these outputs were used to generate motion plans for a \emph{Universal Robotics Ur5e} robot equipped with a pneumatic gripper, a plastic bottle was successfully thrown into a target container located outside the robot's reachable volume. Adequate output sequences were attained with both model architectures at multiple hyperparameter combinations, so to draw specific conclusions the quantitative evaluation metrics discussed in \ref{sec:eval} were computed on the 84 systematically trained models described above.

>>>>

Fig. \ref{fig:vis_exec} illustrates how model outputs were visualized to use their qualitative aspects in guiding hyperparameter choice, and a preliminary implementation on a real robot was achieved -- executing trajectories generated by the simpler feedforward network, with target coordinates sampled from normal distributions corresponding to their values in the training data set. As can be seen, when these outputs were used to generate motion plans for a \emph{Universal Robotics Ur5e} robot equipped with a pneumatic gripper, a plastic bottle was successfully thrown into a target container located outside the robot's reachable volume. Adequate output sequences were attained with both model architectures at multiple hyperparameter combinations, so to draw specific conclusions the quantitative evaluation metrics discussed in \ref{sec:eval} were computed on the 84 systematically trained models described above.
